Path Model Temperature Comparisons

### 2016-07-15 path-temp-compare.Rmd
Add residuals vs. predictor plots for umca density and diversity models.

Using data on oak infection at the plot-level:
```{r hours >25 path model all oak plots unscaled, echo=F}
model_list1 <- list(
      shannons <- lm(H.2005 ~ twi15m.log, data = filter(oakplots.sub, sample_year == 2005)),

@@

Examining the residual plots of each piece of the path model
```{r shannons residuals plot}
par(mfrow=c(2,2))
plot(shannons, main = "OLS regression of diversity ~ wetness index")
```

```{r bay laurel density residuals plot}
plot(umca_density, main = "LMM of bay laurel density")
```

```{r symptomatic leaf count residuals plot}
plot(slc, main = "LMM of symptomatic leaf count")
```

```{r wet-hours residuals plot}
plot(wet_hours_1422, main = "LMM of avg. # of hours 14-22 C current & prev. year")
```

```{r dry-season hours residuals plot}
plot(hrs_abv25, main = "LMM of # of hours >25 C during prev. dry season")
```

```{r oak infection residuals plot}
plot(oak_infection, main = "Binomial GLMM of oak infection")
```

>>>>

@@

```{r hours >25 path model all oak plots unscaled, echo=F}
model_list1 <- list(
      shannons <- lm(H.2005 ~ twi15m.log, data = oakplots.sub),

Examining the residual plots of each piece of the path model
```{r shannons residuals plot}
par(mfrow=c(2,2))
plot(shannons, main = "OLS regression of diversity ~ wetness index residuals")
par(mfrow=c(1,1))
plot(shannons$model$twi15m.log, resid(shannons),
     xlab = "wetness index",
     ylab = "model residuals",
     main = "Diversity model residuals vs. wetness index predictor")
```

```{r bay laurel density residuals plot}
plot(umca_density, main = "LMM of bay laurel density residuals")
plot(umca_density@frame$twi15m.log, resid(umca_density),
     xlab = "wetness index",
     ylab = "model residuals",
     main = "Bay laurel density model residuals vs. wetness index predictor")
```

```{r symptomatic leaf count residuals plot}
plot(slc, main = "LMM of symptomatic leaf count residuals")
```

```{r wet-hours residuals plot}
plot(wet_hours_1422, main = "LMM of avg. # of hours 14-22 C current & prev. year residuals")
```

```{r dry-season hours residuals plot}
plot(hrs_abv25, main = "LMM of # of hours >25 C during prev. dry season residuals")
```

```{r oak infection residuals plot}
plot(oak_infection, main = "Binomial GLMM of oak infection residuals")
```
